InteroceptionScale (study 2) - Data Analysis

### 2025-07-04 paper/manuscript.qmd
minor

```{r}
#| label: fig-four
#| fig-cap: "Correlation Matrices between the Mint dimensions (upper-left), and between the Mint and other interoception questionnaires (MAIA, BPQ and IAS; upper-right). The bottom matrix shows the relationships between interoception and other measures included in the study, such as alexithymia (TAS-20), depression and anxiety (PHQ-4), emotion reactivity (ERS), abnormal and dissociative experiences (CEFSA), and Primal World Beliefs. Stars indicate dimensions that have been score-reversed for better in-context interpretation. Correlation coefficients are shown for significant correlations."
#| fig-align: "center"
#| apa-twocolumn: true  # A Figure Spanning Two Columns When in Journal Mode
#| out-width: "100%"

>>>>

```{r}
#| label: fig-four
#| fig-cap: "Correlation Matrices between the Mint dimensions (upper-left), and between the Mint and other interoception questionnaires (MAIA, BPQ and IAS; upper-right). The bottom matrix shows the relationships between interoception and other measures included in the study, such as alexithymia (TAS-20), depression and anxiety (PHQ-4), emotion reactivity (ERS), abnormal and dissociative experiences (CEFSA), and Primal World Beliefs. Stars indicate dimensions that have been score-reversed for better in-context interpretation. Correlation coefficients are shown only for significant correlations (p < .001)."
#| fig-align: "center"
#| apa-twocolumn: true  # A Figure Spanning Two Columns When in Journal Mode
#| out-width: "100%"

### 2025-07-04 paper/manuscript.tex
minor

\authornote{\par{\addORCIDlink{Dominique
Makowski}{0000-0001-5375-9967}}\par{\addORCIDlink{Ana
Neves}{0009-0006-0020-7599}}\par{\addORCIDlink{Giulia
Poreiro}{0000-0002-2343-5109}} 
\par{ }
\par{     \begin{tcolorbox}[enhanced jigsaw, left=2mm, breakable, colback=white, rightrule=.15mm, colframe=quarto-callout-note-color-frame, toprule=.15mm, bottomrule=.15mm, arc=.35mm, leftrule=.75mm, opacityback=0]

@@

{\caption{{Correlation Matrices between the Mint dimensions
(upper-left), and between the Mint and other interoception
questionnaires (MAIA, BPQ and IAS; upper-right). The bottom matrix shows
the relationships between interoception and other measures included in
the study, such as alexithymia (TAS-20), depression and anxiety (PHQ-4),
emotion reactivity (ERS), abnormal and dissociative experiences (CEFSA),
and Primal World Beliefs. Stars indicate dimensions that have been
score-reversed for better in-context interpretation. Correlation
coefficients are shown for significant
correlations.}{\label{fig-four}}}}

>>>>

\authornote{\par{\addORCIDlink{Dominique
Makowski}{0000-0001-5375-9967}}\par{\addORCIDlink{Ana
Neves}{0009-0006-0020-7599}}\par{\addORCIDlink{Giulia
Poreiro}{0000-0002-2343-5109}} 
\par{ }
\par{     \begin{tcolorbox}[enhanced jigsaw, left=2mm, arc=.35mm, bottomrule=.15mm, leftrule=.75mm, rightrule=.15mm, colback=white, breakable, opacityback=0, colframe=quarto-callout-note-color-frame, toprule=.15mm]

@@

{\caption{{Correlation Matrices between the Mint dimensions
(upper-left), and between the Mint and other interoception
questionnaires (MAIA, BPQ and IAS; upper-right). The bottom matrix shows
the relationships between interoception and other measures included in
the study, such as alexithymia (TAS-20), depression and anxiety (PHQ-4),
emotion reactivity (ERS), abnormal and dissociative experiences (CEFSA),
and Primal World Beliefs. Stars indicate dimensions that have been
score-reversed for better in-context interpretation. Correlation
coefficients are shown only for significant correlations (p \textless{}
.001).}{\label{fig-four}}}}

### 2025-07-04 study2/analysis/2_analysis.qmd
minor

make_cor <- function(df1, df2=NULL, qname_x=TRUE, qname_y=TRUE, textsize = 2.9, xcol = "#424242", ycol="#424242") {

  r <- df1 |> 
    correlation::correlation(data2=df2, p_adjust="none", redundant=ifelse(is.null(df2), TRUE, FALSE)) |> 
    correlation::cor_sort() |>
    mutate(label = ifelse(p < .001, paste0(insight::format_value(r)), ""),
           Parameter1 = cleanlabels(Parameter1, qname=qname_x),
           Parameter2 = cleanlabels(Parameter2, qname=qname_y))
  r[as.character(r$Parameter1) == as.character(r$Parameter2), "label"] <- ""

@@

p_cormint <- make_cor(cbind(mint, metamint), qname_x = FALSE, qname_y = FALSE, textsize = 2.5,
                      xcol = "#00838F", ycol = "#00838F") +
  labs(title="Correlations between MINT dimensions") +
  theme(axis.title = element_blank())

@@

p_corintero <- make_cor(select(df, starts_with("MAIA"), IAS, BPQ),
                        cbind(mint, metamint), qname_y = FALSE, textsize = 2.5,
                        ycol = "#00838F") +
  labs(title="MINT vs. Other Interoception Questionnaires") +
  theme(axis.title = element_blank())
p_corintero
```

@@

```{r}
#| warning: false
#| eval: false

>>>>

make_cor <- function(df1, df2=NULL, qname_x=TRUE, qname_y=TRUE, textsize = 3, xcol = "#424242", ycol="#424242") {

  r <- df1 |> 
    correlation::correlation(data2=df2, p_adjust="none", redundant=ifelse(is.null(df2), TRUE, FALSE)) |> 
    correlation::cor_sort() |>
    mutate(label = ifelse(p < .001, paste0(insight::format_value(r, lead_zero = FALSE, zap_small = TRUE)), ""),
           Parameter1 = cleanlabels(Parameter1, qname=qname_x),
           Parameter2 = cleanlabels(Parameter2, qname=qname_y))
  r[as.character(r$Parameter1) == as.character(r$Parameter2), "label"] <- ""

@@

p_cormint <- make_cor(cbind(mint, metamint), qname_x = FALSE, qname_y = FALSE, textsize = 2.8,
                      xcol = "#00838F", ycol = "#00838F") +
  labs(title="Correlations between MINT dimensions") +
  theme(axis.title = element_blank())

@@

p_corintero <- make_cor(select(df, starts_with("MAIA"), IAS, BPQ),
                        cbind(mint, metamint), qname_y = FALSE, textsize = 2.8,
                        ycol = "#00838F") +
  labs(title="MINT vs. Other Interoception Questionnaires") +
  theme(axis.title = element_blank())
p_corintero
```

@@

```{r}
#| warning: false
#| eval: true
